Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-27 paper/main.tex
rewrite list as algorithm

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{float}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathrsfs}
\usepackage{onimage}
\usepackage{graphicx}
\usepackage{doi}
\usepackage{acronym}
\usepackage[right]{lineno}
\usepackage{listings}
\usepackage[mode=buildnew]{standalone}
\usepackage{tikz}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{cite}
\usepackage{acronym}
\usepackage{xcolor}

@@

Having defined the input type of our algorithm, we proceed with the following 5 steps:
\textbf{TODO possibly restructure this as an algorithm instead of list}
\begin{enumerate}
    \item Obtain submasks for each cell individually.
    \item Skeletonize submask with algorithm from Lee~\cite{Lee1994}
    \item Determine endpoints $\vec{q}_0,\vec{q}_1$.
        Assert that there are only 2 endpoints.
    \item Sort points such that they form a polygon.
    \item Interpolate vertices $\vec{x}_i$ from obtained polygon.
\end{enumerate}

In the first step, the image will be split into a collection of subimages that only contain
information for one single cell.
From there, we apply a skeletonization algorithm~\cite{Lee1994}
(Figure~\ref{fig:position-extraction-algorithm} (C)).
It has to be noted that there are multiple variants of skeletonization and in general, these classes
of algorithms can produce results which have intersection points and multiple endpoints, which is
undesirable in our case.
We have found that for most practical examples, the algorithm devised by~\cite{Lee1994} works well.\\

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{float}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{onimage}
\usepackage{graphicx}
\usepackage{doi}
\usepackage{acronym}
\usepackage[right]{lineno}
\usepackage{listings}
\usepackage[mode=buildnew]{standalone}
\usepackage{tikz}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{cite}
\usepackage{acronym}
\usepackage{xcolor}

@@

% Having defined the input type of our algorithm, we proceed with the following 5 steps:

\begin{algorithm}
    \caption{Position Extraction Algorithm}
    \label{algo:extraction-algorithm}
    \begin{algorithmic}[1]
        \Function{Extraction}{\texttt{mask}, \texttt{n\_vertices}}
        \State $\texttt{positions} \gets [\hspace{6pt}]$
        \Comment{Initialzie empty array}
        \For{\texttt{color $\in$ colors(mask)}}
            \State $\texttt{submask} \gets \texttt{mask}$% \Comment{Obtain submask for each cell}
            \For{$\texttt{pixel}\in\texttt{submask}$
                \Comment{Only retain \texttt{background} and \texttt{color}}
                \If{$\texttt{pixel}\neq\texttt{color}$}}
                    \State $\texttt{pixel}\gets\texttt{background}$
                    \Comment{Background is $(0,0,0)$ in \texttt{RGB}}
                \EndIf
            \EndFor
            \State $\mathrlap{\texttt{skeleton}}\hphantom{\texttt{verticess}} \gets \texttt{skeletonization}_\text{Lee}(\texttt{submask})$
            \Comment{Method by Lee~\cite{Lee1994}}
            \State $\mathrlap{\texttt{ends}}\hphantom{\texttt{verticess}} \gets \texttt{endpoints}(\texttt{skeleton})$
            \If{$\#\texttt{ends}\neq2$}
                \State \textit{Routine Fails}
            \EndIf
            \State $\mathrlap{\texttt{polygon}}\hphantom{\texttt{verticess}} \gets \texttt{sort\_points}(\texttt{skeleton},\texttt{ends})$
            \Comment{Between endpoints}
            \State $\mathrlap{\texttt{vertices}}\hphantom{\texttt{verticess}} \gets \texttt{interpolate\_}(\texttt{polygon}, \texttt{n\_vertices})$
            \State $\texttt{append}(\texttt{positions}, \texttt{vertices})$
        \EndFor
        \State \Return \texttt{positions}
        \EndFunction
    \end{algorithmic}
\end{algorithm}

Algorithm~\ref{algo:extraction-algorithm} shows the performed steps which allow us to obtain
vertices for individual bacteria.
It requires a segmented image and a desired number of vertices to obtain as inputs.
In the first step, the image will be split into a collection of subimages that only contain
information for one single cell.
From there, we apply a skeletonization algorithm~\cite{Lee1994}
(Figure~\ref{fig:position-extraction-algorithm} (C)).
It has to be noted that there are multiple variants of skeletonization and in general, these classes
of algorithms can produce results which have intersection points and multiple endpoints, which is
undesirable in our case.
We have found that for most practical examples, the algorithm devised by~\cite{Lee1994} works well.\\
